---
title: "Vis_Project"
author: "Sulagna Barat"
date: "2022-11-02"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## **ABSTRACT**

The main goal of this project is to provide a Visual representation of Human Development Index and Inequality-Adjusted HDI scenario to comparatively gauge a country’s spectrum of progress or on the other hand sole triggers of lagging behind, so as to initiate preventive measures to address the burning issues of today’s human civilization.
We will be visualizing various Uni-variate and Multivariate plots to understand the relationship between the variables. Also, we will draw some Time series based charts to witness how the HDI has changed over time.

## **CONTENTS**

* *Introduction*
* *About the Data Set*
* *Working Variables*
* *The Objective of the Project*
* *Analysis*
* *Conclusion*

## **INTRODUCTION**
 
My project comprises three parts. It revolves around providing a comparative study:-

1. Among different components of HDI such that Life Expectancy at Birth, Expected & Mean Years of Schooling, GNI Per Capita.
2. Among different components of IHDI such that Inequality adjusted Life Expectancy at Birth, Education & Income.
3. Lastly, a 30 year Trend Analysis of HDI among different countries.

## **ABOUT THE DATA SET**

The data sets I am working on are:-

1. Human Development Index and its components 
2. Inequality-adjusted Human Development Index 
Source: https://hdr.undp.org/data-center/documentation-and-downloads

# **WORKING VARIABLE**

 Variable Name	|     Type	          |     Description
 -------------  |-------------------- |-------------------
Country     	|Categorical (Nominal)|Country name
Life Expectancy (at birth)	        | Numeric(Continuous)| Assumed longevity(2021)
Expected Years of Schooling	          | Numeric(Continuous)|	  |Attaining education(2021)
GNI per capita       	  |Numeric(Discrete)  |Individual gross national income (2017 PPP$)
HDI Value 	| Numeric(Continuous)  |Human Development Index
Inequality-adjusted Life Expectancy 	        | Numeric(Continuous)| Inequality discounted assumed longevity (2021)
Inequality-adjusted Education          | Numeric(Continuous)||Inequality discounted attainment of education (2021)
Inequality-adjusted Income          | Numeric(Continuous)||Inequality discounted earning (2021)
Gini Coefficient   	|Numeric(Continuous)	| Wealth inequality reflector (2010-2021)

## **THE OBJECTIVE OF THE PROJECT**

*   *Extractions from HDI*
 1. Among the groups of very high, high, medium & low developed nations, which are the respective best and worst in terms of life expectancy, excepted schooling year & per capita GNI?
 2. Changes in HDI rankings for two consecutive years.
 3. Trend of change over years.
    
    
*   *Extractions from IHDI*
 1. Among the groups of very high, high, medium & low developed nations, which are the respective best & worst in terms of inequality-adjusted life expectancy, education & income?
 2. Among the aforementioned, where does the wealth inequality prevail the most? 
 3. Income shareholding scenario.

```{r}
data=read.csv("VHD_HDI.csv")
library(ggplot2)
ggplot(data,aes(x=Country,y=Expectancy_2021,fill=Country))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="Life Expectancy at birth (2021) for Very Highly Developed Countries")
```

```{r}
```


```{r}
data=read.csv("VHD_HDI.csv")
ggplot(data,aes(x=Countries,y=Values,fill=Schooling))+
  geom_bar(stat="identity", position="dodge")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="Expected vs Mean Schooling Years for Very Highly Developed Countries")
```


```{r}
```


```{r}
data=read.csv("VHD_HDI.csv")
ggplot(data,aes(x=Country,y=GNI_per_capita_2021,fill=Country))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="GNI per Capita (2021) for Very Highly Developed Countries")
```

```{r}
data=read.csv("VHD_HDI.csv")
ggplot(data,aes(x=Countries,y=HDI,fill=Years))+
  geom_bar(stat="identity", position="dodge")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="HDI Rank of Very Highly Developed Countries for two consecutive years")
```
```{r}
data=read.csv("HD_HDI.csv")
library(ggplot2)
ggplot(data,aes(x=Country,y=Expectancy_2021,fill=Country))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="Life Expectancy at birth (2021) for Highly Developed Countries")
```
```{r}
data=read.csv("HD_HDI.csv")
ggplot(data,aes(x=Countries,y=Values,fill=Schooling))+
geom_bar(stat="identity", position="dodge")+
theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="Expected vs Mean Schooling Years for Highly Developed Countries")
```
```{r}
data=read.csv("HD_HDI.csv")
ggplot(data,aes(x=Country,y=GNI_per_capita_2021,fill=Country))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="GNI per Capita (2021) for Highly Developed Countries")
```


```{r}
data=read.csv("HD_HDI.csv")
ggplot(data,aes(x=Countries,y=HDI,fill=Years))+
  geom_bar(stat="identity", position="dodge")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="HDI Rank of Highly Developed Countries for two consecutive years")
```
```{r}
data=read.csv("3MD.csv")
library(ggplot2)
ggplot(data,aes(x=Country,y=Gini_coefficient_2010_2021,fill=Country))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="Gini Coefficient for Medium Developed Countries (2010-2021)")
```
```{r}
data=read.csv("3MD.csv")
ggplot(data,aes(x=Countries,y=Values,fill=Inequality_adjusted_index_2021))+
  geom_bar(stat="identity", position="dodge")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="Categorical IHDI for Medium Developed Countries")
```

```{r}
data=read.csv("3MD.csv")
ggplot(data,aes(x=Countries,y=Val,fill=Index))+
  geom_bar(stat="identity", position="dodge")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="HDI vs IHDI for Medium Developed Countries")
```
```{r}
data=read.csv("4LD.csv")
library(ggplot2)
ggplot(data,aes(x=Country,y=Gini_coefficient_2010_2021,fill=Country))+
  geom_bar(stat="identity")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="Gini Coefficient for Low Developed Countries (2010-2021)")
```
```{r}
data=read.csv("4LD.csv")
ggplot(data,aes(x=Countries,y=Values,fill=Inequality_adjusted_index_2021))+
  geom_bar(stat="identity", position="dodge")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="Categorical IHDI for Low Developed Countries")
```

```{r}
data=read.csv("4LD.csv")
ggplot(data,aes(x=Countries,y=Val,fill=Index))+
  geom_bar(stat="identity", position="dodge")+
  theme(axis.text.x=element_text(angle=90,hjust=1))+labs(title="HDI vs IHDI for Low Developed Countries")
```

Hence the conclusion follows.